Supplementary material

### 2018-08-18 paper/letter/letter.tex
sample added

    }

@@

    \reply{The specific region used for the analysis is irrelevant to the
    method, we could have used mixed regions for instance. We adopted CTs
    because it is the most finely grained data available including more than
    population count. Additionally, other census areas do not change as
    frequently as CTs. }

    \textbf{Revision Required:}
    Figure 2: while useful could use more detail and better explanation of the
    algorithm, it could do a better job in showing clustering and explaing the diagram
    since this is the figure that explains the entire paper.
}
\end{itemize}

@@

    In this paper, the authors propose a method for longitudinal data analysis that
    avoids the geographical harmonization. The paper focuses on an interesting topic.
    The weakness of the paper is that the motivation and design requirements are not
    clearly demonstrated, and the design process is not justified.}

@@

@@

    In Section 4.2, the authors proposed a graph based geographic content clustering,
    which considers spatial, temporal, and similarity information among regions. Here,
    it will be worth to conducting comparisons with some traditional methods, for
    example, k-means purely based on histogram distances or weighted distance by
    considering spatio-temporal information (specific for the first one, since I think
    there is a high correlation of spatio-temporal information with the histogram
    distance).
    \reply{TODO}
    }

@@

    \reply{Colour assignment was indeed challenge for this work, mostly because
    it needs to be used, but there isn't a definitive way to actually do it.
    That was also the reason for artificially limiting the maxium number of
    clusters to eight. There is indeed overlap between the colours used for
    relevance and the clusters, mostly because the clusters used virtually all
    of the colour space. However, we believe that their different meanings are
    clear, since none of the experts, nor the other reviewers, mentioned any
    confusion in this specific aspect. It is not ideal, but we believe it is a
    acceptable approximation.}}

@@

    \reply{Following the guidelines, an application paper doesn't need to
    include new techniques. Indeed, the objective of this work was to leverage
    "commonplace" VIS methods to provide a more efficient solution to a common
    issue in another field. Indeed, we provide a viable alternative to time
    consuming and challenging problem that was believed to be unavoidable.}}

@@

    \reply{Unfortunately the reviewer doesn't mention which is the "most related
    work". I did review some works from Andrienko's group, after all they are
    fairly known for this, but some were not included because they are not
    relevant to the current problem. TODO I included more text expliciting
    exactly what was accomplished in this work, which hopefully will make that
    distinction clearer. \\ As the others reviewers mentioned, the tool was
    available not only for the experts, but for the reviewers as well, on an
    anonymous site.}

@@

    \begin{itemize}
        \item{The design consideration of M1 \& M2 are too general, could be
        said for most urban visual analytics methods}
        \item{Last paragraph of Section 4.2, why augment two edges, any quantitative
        evident/support from data?}
        \item{Figure 4 could be put at page 4 for better viewing experience}
        \item{Section 4.6, Sect. to Sec., on top left to on the top left}
        \item{It will be helpful to put a sample census data in the paper, e.g., a table}
        \item{The Sankey diagram in Figure 6 is cluttered, any solution?}
    \end{itemize}

>>>>

    \reply{We added/expanded discussion about the choices, including the
     subsection about color.}}

    \item{Motivation: the authors fail to clearly demonstrate the motivation of their
    work, probably due to their writing style. (R2, R4)}
    \reply{The introduction was re-written to make this clearer.}

@@

    \reply{The specific region used for the analysis is irrelevant to the
    method, we could have used mixed regions for instance. We adopted CTs
    because it is the most finely grained and volatile data available including
    more than population count. And all the communications with the experts was
    included in the supplementary material.}

    \textbf{Revision Required:}
    Figure 2: while useful could use more detail and better explanation of the
    algorithm, it could do a better job in showing clustering and explaing the diagram
    since this is the figure that explains the entire paper.

    \reply{This change wasn't made because we do not introduce the clustering
    algorithm. For the purposes of this work, any hierarchical clustering would
    work.}}
\end{itemize}

@@

    In this paper, the authors propose a method for longitudinal data analysis that
    avoids the geographical harmonization. The paper focuses on an interesting topic.
    The weakness of the paper is that the motivation and design requirements are not
    clearly demonstrated, and the design process is not justified.

    \reply{The intro was re-written and justifications/discussions added for every plot/option.}
    }

@@

    \reply{The introduction was re-written to make this explicit.}

@@

    In Section 4.2, the authors proposed a graph based geographic content clustering,
    which considers spatial, temporal, and similarity information among regions. Here,
    it will be worth to conducting comparisons with some traditional methods, for
    example, k-means purely based on histogram distances or weighted distance by
    considering spatio-temporal information (specific for the first one, since I think
    there is a high correlation of spatio-temporal information with the histogram
    distance).

    \reply{We did not propose a new clusering method. Any hierarchical
    clustering would work, with potentially minimal differences in the result.
    This specific suggestion corresponds to the ClustGeo, an R package that does
    Ward clustering with two distance matrices to express geographic distance.
    That work is mentioned and discussed.}}

@@

    \reply{Colour assignment was indeed challenge for this work, mostly because
    it needs to be used, but there isn't a definitive way to actually do it.
    That was also the reason for artificially limiting the maxium number of
    clusters to eight. There is indeed overlap between the colours used for
    relevance and the clusters, mostly because the clusters used virtually all
    of the colour space. However, we believe that their different meanings are
    clear, since none of the experts, nor the other reviewers, mentioned any
    confusion in this specific aspect. It is not ideal, but we believe it is a
    acceptable approximation. Not ideal, but reasonable enough.}}

@@

    \reply{This is an application paper, not a technique paper. It's objective
    is to demonstrate how cleverly combining simple, well explored, VIS methods
    can solve an "unsolvable" problem for demographic analysis. All the panels
    contain established tools (except for the "enhanced" boxplot, I didn't find
    anything similar in the literature, but that's hardly the main contribution
    of the paper).}

@@

    \reply{Unfortunately the reviewer doesn't mention which is the "most related
    work". I did review some works from Andrienko's group, after all they are
    fairly known for this, but some were not included because they are not
    relevant to the current problem. \\The introduction and related work were
    re-written and significantly expanded. I included more text expliciting
    exactly what was accomplished in this work, which hopefully will make that
    distinction clearer. \\ As the others reviewers mentioned, the tool was
    available not only for the experts, but for the reviewers as well, on an
    anonymous site.}

@@

    \begin{itemize}
        \item{The design consideration of M1 \& M2 are too general, could be
        said for most urban visual analytics methods}
        \item{Last paragraph of Section 4.2, why augment two edges, any quantitative
        evident/support from data?}
        \item{Figure 4 could be put at page 4 for better viewing experience}
        \item{Section 4.6, Sect. to Sec., on top left to on the top left}
        \item{It will be helpful to put a sample census data in the paper, e.g., a table}
        \item{The Sankey diagram in Figure 6 is cluttered, any solution?}
    \end{itemize}
    \reply{We removed the design objectives. Indeed they were rather obvious for
    the context/application. \\
    The discussion for edge augmentation was extended.\\
    Figure placement is up to latex, and the publishers.\\
    The data for a single CT would occupy too much space. It is included in the
    supplementary material.}

### 2018-08-18 sup/sup.tex
alpha
name update
sample added

\documentclass[a4paper]{article}  
\usepackage{url}
\usepackage{hyperref}
\title{Supplementary material}
\author{}
\date{}
\ifpdf%                                % if we use pdflatex
  \pdfoutput=1\relax                   % create PDFs from pdfLaTeX
  \pdfcompresslevel=9                  % PDF Compression
  \pdfoptionpdfminorversion=7          % create PDF 1.7
  \ExecuteOptions{pdftex}
  \usepackage{graphicx}                % allow us to embed graphics files
  \DeclareGraphicsExtensions{.pdf,.png,.jpg,.jpeg} % for pdflatex we expect .pdf, .png, or .jpg files
\else%                                 % else we use pure latex
  \ExecuteOptions{dvips}
  \usepackage{graphicx}                % allow us to embed graphics files
  \DeclareGraphicsExtensions{.eps}     % for pure latex we expect eps files
\fi%
\graphicspath{{figures/}{pictures/}{images/}{./}} % where to search for the images

@@

\subsection{B - Ethan A. Fosse}
% \href{https://scholar.harvard.edu/ethanfosse}{\url{https://scholar.harvard.edu/ethanfosse}}
\emph{Research Associate at Princeton University, USA}

@@

I really like the idea of the colours having the additional tag of the feature
that defines them more clearly on the left. However, once one starts playing
around with the platform using several variables at the same time, things become
tricky to interpret. For example, in Vancouver, things seem to change
dramatically from all green to all orange. This is highlighted by the graph of
trajectories in which the population involved in each cluster is nested in
colours. Once one gets into the data, the changes don’t look so sharp after all
(maybe in education and income). This may not be a problem of the platform as it
is, but there may be a warning regarding that the “severity” of changes is not
necessarily the same across cities.

@@

>>>>

\documentclass[a4paper]{article}  
\usepackage{url}
\usepackage{hyperref}
\usepackage{multirow}
\title{Supplementary material}
\author{}
\date{}
\ifpdf%                                % if we use pdflatex
  \pdfoutput=1\relax                   % create PDFs from pdfLaTeX
  \pdfcompresslevel=9                  % PDF Compression
  \pdfoptionpdfminorversion=7          % create PDF 1.7
  \ExecuteOptions{pdftex}
  \usepackage{graphicx}                % allow us to embed graphics files
  \DeclareGraphicsExtensions{.pdf,.png,.jpg,.jpeg} % for pdflatex we expect .pdf, .png, or .jpg files
\else%                                 % else we use pure latex
  \ExecuteOptions{dvips}
  \usepackage{graphicx}                % allow us to embed graphics files
  \DeclareGraphicsExtensions{.eps}     % for pure latex we expect eps files
\fi%
\graphicspath{{figures/}{pictures/}{images/}{./}} % where to search for the images

@@

\subsection{B - Ethan Fosse}
% \href{https://scholar.harvard.edu/ethanfosse}{\url{https://scholar.harvard.edu/ethanfosse}}
\emph{Research Associate at Princeton University, USA}

@@

I really like the idea of the colours having the additional tag of the feature
that defines them more clearly on the left. However, once one starts playing
around with the platform using several variables at the same time, things become
tricky to interpret. For example, in Vancouver, things seem to change
dramatically from all green to all orange. This is highlighted by the graph of
trajectories in which the population involved in each cluster is nested in
colours. Once one gets into the data, the changes don't look so sharp after all
(maybe in education and income). This may not be a problem of the platform as it
is, but there may be a warning regarding that the “severity” of changes is not
necessarily the same across cities.

@@

\clearpage
\section{Data samples}
\subsection{Canada}
Data for one CT over time in Toronto.
\begin{center}
  \includegraphics[width=\linewidth]{SampleCA.png}
  \input{tableCA}
  \end{center}

\clearpage

\subsection{USA}
Data for one CT over time in Brooklyn.
\begin{center}
  \includegraphics[width=\linewidth]{SampleUS.png}
  \input{tableUS}
\end{center}
